Reasoning About a Machine with Local Capabilities

### 2018-05-11 toplas/paper.tex
minor edits and comments on proof of awkward example

  As described in \sectionname~\ref{sec:reasoning}, we use the FTLR (Theorem~\ref{thm:ftlr}) to reason about unknown code, so we use it to reason about $c_\adv$.
  With the standard region $\iota^{nwl,p}$ chosen for the adversary, it is easy to show that the $\readCond{}$ and $\writeCond{}$ holds for $c_\adv$ which gives us $c_\adv \in \stder(W)$ by the FTLR.
  In order to get \ref{eq:g1:main-O-res}, we need to show that (a) the memory satisfies the world and (b) the register file is in the $\stdrr(W)$.
  We have defined the world, so there (almost) is a one-to-one correspondence between region and memory segment in the initial configuration, so (a) is easily shown.
  In order to show (b), we need to show $c_\stk \in \stdvr(W)$ and $c_{g1} \in \stdvr(W)$.
  The former follows easily from the choice of a $\iota^{pwl}$-region for the stack in $W$.
  In order to argue the latter, we basically have to argue that $c_{g1}$, the closure generator, respects the world $W$.
  This amounts to showing that the closures generated by \texttt{g1} also respect the invariants of $W$.
  The reasoning concerning variable $x$ follows that of \citet{Dreyer:jfp12}, so we will ignore it in the remainder of the proof and focus on the reasoning related to this low-level scenario.

@@

  We need to argue that it is safe to give the return pointer that \texttt{scall} constructs to the adversary which correspond to reason about the remainder of the execution of \texttt{f4} (corresponding to the Hyp-Cont case of the \texttt{scall} lemma).
  The return pointer is a local capability, so we may assume that it is invoked in some configuration that satisfies $W_3 \futurewk W_2$.
  This means that none of the temporary regions have been revoked, so the regions we replaced the old stack region with are still present in $W_3$.
  We know exactly how the execution proceeds upon return (the recovery code is executed, and $x$ is set to 0), so for the part of the execution up until the \texttt{scall} we once again use the anti-reduction lemma.

  For the \texttt{scall} itself we of course apply the \texttt{scall} lemma.
  As the private stack has changed, we need to replace the two regions that govern the stack.
  This means that the second invocation of the callback takes place in a world $W_4 \futurestr W_3$.
  The reasoning about \texttt{scall} is the same as for the first callback invocation.
  The callback capability is still safe because it is global which basically covers the Hyp-Callee case.
  For the Hyp-Cont case, we get a world $W_5 \futurewk W_4$ in which we need to argue that the remainder of the execution is safe.
  At this point, we can use the anti-reduction lemma a final time to get to the point where we jump to the return pointer.

  If we can argue that it is safe to jump to the return pointer that we got initially from the adversary, then the proof is done.
  We have made no checks on the return pointer, so we have no idea whether it is local or global\footnote{We may assume that it is a capability that is executable when jumped to otherwise the execution fails which is considered safe.}.
  W.l.o.g.\ assume the return pointer is local.
  This means that it is safe in public future worlds of $W_1$ (remember that it came from $\reg$ and $\reg \in \stdrr(W_1)$).
  This means that we need to construct a world $W_6$ with all the temporary and revoked regions of $W_1$ (this corresponds to restoring the invariants the adversary relies on for its safe execution).
  Further for all these regions, $W_6$ must use the same region names as $W_1$ for $W_6$ to be a public future world.
  As we used the anti-reduction lemma to get to this point, $W_6$ must also be constructed to be a private future world of $W_5$.
  Before we construct $W_6$, let us consider where each of the worlds we have seen so far came from: As illustrated in \figurename~\ref{fig:worlds-in-pf-g1}, we constructed $W_2$ and $W_4$ which are the only private future worlds we have considered so far.
  This means that we know exactly what changes they made.
  In particular, we did not mask any of the temporary or revoked regions in $W_1$ with a permanent region.
  This means that in $W_6$, we can reinstate every temporary or revoked region of $W_1$.
  In the private future worlds we constructed, we only took transitions that, relative to $W_1$, are public.
  The worlds we were given, $W_3$ and $W_5$ may have taken arbitrary public transitions, but this is no problem with respect to the public future world relation.
  In $W_5$ there were regions to handle the stack.
  These regions obviously need to be revoked as the $W_1$ stack regions replace them.
  The non-stack regions in $W_5$ that are not present in $W_1$ are also added in $W_6$, which the public future world relation permits as it is extensional.
  All in all, it is possible to construct $W_6$, so it is both a public future world of $W_1$ and a private world of $W_5$ which means that it is indeed safe to return to the adversary.

>>>>

  As described in \sectionname~\ref{sec:reasoning}, we use the FTLR (Theorem~\ref{thm:ftlr}) to reason about unknown code, so we use it to reason about $c_\adv$.
  With the standard region $\iota^{nwl,p}$ chosen for the adversary, it is easy to show that the $\readCond{}$ and $\writeCond{}$ holds for $c_\adv$ which gives us $c_\adv \in \stder(W)$ by the FTLR.
  In order to get \eqref{eq:g1:main-O-res}, we need to show that (a) the memory satisfies the world and (b) the register file is in the $\stdrr(W)$.
  We have defined the world, so there (almost) is a one-to-one correspondence between region and memory segment in the initial configuration, so (a) is easily shown.
  In order to show (b), we need to show $c_\stk \in \stdvr(W)$ and $c_{g1} \in \stdvr(W)$.
  The former follows easily from the choice of a $\iota^{pwl}$-region for the stack in $W$.
  In order to argue the latter, we basically have to argue that $c_{g1}$, the closure generator, respects the world $W$.
  This amounts to showing that the closures generated by \texttt{g1} also respect the invariants of $W$.
  The reasoning concerning variable $x$ follows that of \citet{Dreyer:jfp12}, so we will ignore it in the remainder of the proof and focus on the reasoning related to this low-level scenario. \lars{preceding sentence is unclear: what is $x$, what does ``this low-level scenario'' refer to ?}

@@

  We need to argue that it is safe to give the return pointer that \texttt{scall} constructs to the adversary which corresponds to reasoning about the remainder of the execution of \texttt{f4} (corresponding to the Hyp-Cont case of the \texttt{scall} lemma).
  The return pointer is a local capability, so we may assume that it is invoked in some configuration that satisfies $W_3 \futurewk W_2$.
  This means that none of the temporary regions have been revoked, so the regions we replaced the old stack region with are still present in $W_3$.
  We know exactly how the execution proceeds upon return (the recovery code is executed, and $x$ is set to 0), so for the part of the execution up until the \texttt{scall} we once again use the anti-reduction lemma.

  For the \texttt{scall} itself we, of course, apply the \texttt{scall} lemma.
  As the private stack has changed, we need to replace the two regions that govern the stack.
  This means that the second invocation of the callback takes place in a world $W_4 \futurestr W_3$.
  The reasoning about \texttt{scall} is the same as for the first callback invocation.
  The callback capability is still safe because it is global which basically covers the Hyp-Callee case.
  For the Hyp-Cont case, we get a world $W_5 \futurewk W_4$ in which we need to argue that the remainder of the execution is safe.
  At this point, we can use the anti-reduction lemma a final time to get to the point where we jump to the return pointer.

  If we can argue that it is safe to jump to the return pointer that we got initially from the adversary, then the proof is done.
  We have made no checks on the return pointer, so we have no idea whether it is local or global\footnote{We may assume that it is a capability that is executable when jumped to since otherwise the execution fails which is considered safe.}.
  W.l.o.g.\ assume the return pointer is local.
  This means that it is safe in public future worlds of $W_1$ (remember that it came from $\reg$ and $\reg \in \stdrr(W_1)$).
  Hence we need to construct a world $W_6$ with all the temporary and revoked regions of $W_1$ (this corresponds to restoring the invariants the adversary relies on for its safe execution).
  Further, for $W_6$ to be a public future world, for all these regions, $W_6$ must use the same region names as $W_1$. 
  As we used the anti-reduction lemma to get to this point, $W_6$ must also be constructed to be a private future world of $W_5$.
  Before we construct $W_6$, let us consider where each of the worlds we have seen so far came from: As illustrated in \figurename~\ref{fig:worlds-in-pf-g1}, we constructed $W_2$ and $W_4$ which are the only private future worlds we have considered so far.
  This means that we know exactly what changes they made.
  In particular, we did not mask any of the temporary or revoked regions in $W_1$ with a permanent region.
  This means that in $W_6$, we can reinstate every temporary or revoked region of $W_1$.
  In the private future worlds we constructed, we only took transitions that, relative to $W_1$, are public.
  The worlds we were given, $W_3$ and $W_5$ may have taken arbitrary public transitions, but this is no problem with respect to the public future world relation.
  In $W_5$ there were regions to handle the stack.
  These regions obviously need to be revoked as the $W_1$ stack regions replace them.
  The non-stack regions in $W_5$ that are not present in $W_1$ are also added in $W_6$, which the public future world relation permits as it is extensional.
  All in all, it is possible to construct $W_6$, so it is both a public future world of $W_1$ and a private world of $W_5$ which means that it is indeed safe to return to the adversary.
